Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-16 paper.tex
Update paper.tex

>>>>

Notes for review:

Genome scan of hybridizing sunflowers from Texas
(Helianthus annuus and H. debilis) reveals asymmetric
patterns of introgression and small islands of genomic
differentiation:

In contrast, coalescent analyses of long-term migration
rates imply that interspecific migration has been
more important than mutation in providing new genetic
variation in ssp. texanus populations. Immigration from
H. debilis cucumerifolius into ssp. texanus (M = 4.05;
Nem = 1.74) is higher than median estimates of intraspecific
migration rates in plants (Morjan and Rieseberg 2004) 
and only slightly lower than immigration from
ssp. annuus into ssp. texanus (M = 5.00). Immigration
rates from ssp. texanus into H. debilis cucumerifolius and
ssp. annuus are still higher (M = 6.30 and 7.29, respectively),
implying that the putative hybrid lineage serves
as a bridge for migration between the parental species.

One puzzle is
that the estimated immigration rate between the allopatric
taxa (H. debilis cucumerifolius and ssp. annuus) is
approximately comparable with that between the sympatric
taxa (H. debilis cucumerifolius and ssp. texanus ssp.
texanus). This observation may point to the effectiveness
of ssp. texanus as a bridge for the transfer of alleles
between H. debilis and ssp. annuus. An alternative explanation
is that the BAYESASS estimates are unreliable
because homoplasy of microsatellite alleles is high in
taxa with large-effective population sizes (Estoup et al.
2002) such as the annual sunflowers studied here.

Despite the apparent discrepancy between the results
from STRUCTURE and BAYEASS, several conclusions
can be made. Analyses with STRUCTURE support the
distinctness of ssp. texanus, as well as its clear inclusion
within H. annuus, as initially postulated by Heiser (1951).
Likewise, the STRUCTURE, MIGRATE-N and BAYESASS
analyses all confirm previous report of introgression
between H. annuus and H. debilis (Rieseberg et al.
1990, 2007) and suggest that the introgression is genomewide
when it occurs. Contrary to the Heiser’s scenario of
a recent Holocene origin of ssp. texanus, however, our
results are more consistent with a much longer history of
contact between H. annuus and H. debilis. Otherwise, it is
difficult to account for the presence of significant longterm
migration between currently allopatric populations
of ssp. annuus and H. debilis cucumerifolius. This revised
scenario makes sense in the light of numerous glacialinterglacial
cycles over the past million years (Hewitt
2000), which probably resulted in intermittent contact
between H. annuus and H. debilis, with the last contact
likely occurring during the Wisconsin glaciation,
18 000 BP. The current contact between the species differs
from the previous ones in that it appears to have been
human-aided. Possibly, some of the molecular evidence
of introgression, particularly into allopatric populations,
stems from past periods of contact.

One of the four outlier loci, HT0414, is associated
with a heat-shock protein and was previously shown to
have been the target of selection in H. annuus ssp. annuus
salt marsh populations from the state of Utah
(Kane and Rieseberg 2007), as well as in weedy sunflower populations
from several different locations across the USA
(Kane and Rieseberg 2008). In this study, populations of
ssp. annuus from Kansas, Nebraska and Oklahoma
monomorphic for a single allele, whereas populations
of H. debilis and other populations of ssp. annuus are
considerably more polymorphic. These results imply
that HT0414 may be involved in adaptation to a range
of different habitats or to conditions shared by several
different habitats (Kane and Rieseberg 2008).
